### 2014-10-26 thesis/method/selection.tex
Misc changes to preprocessing and selection
Change 'conclusion' heading in chapter to 'summary'

\section{Preliminary Removal of Features}
We began the process of feature selection by removing attributes that were
not available upon admission, as these tended to be highly related to the
\texttt{los48} outcome and were a consequence, not a predictor, of LOS. Had
we not removed these features, they would be selected by the feature selection
methods described below due to their high association with \texttt{los48}, but
would actually tell us nothing about what causes a patient to require a
hospital stay of more or less than 2 days.
These attributes were: \texttt{iculos}, \texttt{outcome},
\texttt{disp from ed}, \texttt{disp from hosp}, \texttt{died}, \texttt{rehab},
\textit{los} and \texttt{eddc}.
The \texttt{id} attribute was also removed because it
simply numbered each record and
indicated nothing about the patient. This left us with 69 attributes.

@@

\section{Conclusion}
In this chapter we covered feature selection, which is concerned with reducing
the number of attributes that a learning algorithm needs to consider when
trying to learn a relationship between the training examples and their labels.
We described how we removed redundant and meaningless features before the
feature selection step, and discussed the automatic and manual feature
selection methods we use in our work. The value in using several methods of
each type of feature selection is two-fold: it allows us to not only compare
the performance of the methods, but also to compare the performance of the
different classifiers we use independently of the feature selection method.

>>>>

\section{Preliminary Removal of Features}
We began the process of feature selection by removing attributes that were
not available upon admission, as these tended to be highly related to the
\texttt{los48} outcome and were a consequence, not a predictor, of LOS. Had
we not removed these features, they would be selected by the feature selection
methods described below due to their high association with \texttt{los48}, but
would actually tell us nothing about what causes a patient to require a
hospital stay of more or less than 2 days.
These attributes were: \texttt{iculos}, \texttt{outcome},
\texttt{disp from ed}, \texttt{disp from hosp}, \texttt{died}, \texttt{rehab},
\texttt{los} and \texttt{eddc}.
The \texttt{id} attribute was also removed because it
simply numbered each record and
indicated nothing about the patient. This left us with 69 attributes.

@@

\section{Summary}
In this chapter we covered feature selection, which is concerned with reducing
the number of attributes that a learning algorithm needs to consider when
trying to learn a relationship between the training examples and their labels.
We described how we removed redundant and meaningless features before the
feature selection step, and discussed the automatic and manual feature
selection methods we use in our work. The value in using several methods of
each type of feature selection is two-fold: it allows us to not only compare
the performance of the methods, but also to compare the performance of the
different classifiers we use independently of the feature selection method.
